\documentclass[11pt]{article}
\usepackage[margin=2cm]{geometry}
\usepackage{hyperref}
\title{1 - Binary and logic}
\author{Eric Mayhew \& Jacob Errington}
\date{}
\newcommand{\cwurl}{https://www.computing-workshop.com/}
\newcommand{\cwpdf}{\cwurl pdf/}

\begin{document}
\maketitle
This lesson provides its participants with an introduction to transistors and
binary. Understanding binary and transistors are at the core of computers,
therefore it is essential they are discussed in order to be comfortable with
computers. By implementing logic gates using breadboards, participants will learn how basic circuits are
constructed using hands-on learning activities. Understanding circuitry will lay the ground work for
introducing more complicated concepts like integrated circuits and processors in later lessons.

\section*{Overview}

\begin{description}
  \item[Lesson Objectives] ~

   By the end of the lesson, students will be able to:

  \begin{itemize}

    \item Describe how transistors work;

    \item Build basic logic gates out of transistors, both theoretically and
      physically on a breadboard.

  \end{itemize}

  \item [Materials]~

    To run this lesson, the following are needed:

    \begin{itemize}
      \item
        lesson slides;

        \url{\cwpdf 1-presentation.pdf}

      \item
        one breadboard for each group and enough of the following electronic
        components:
        NPN transistors,
        10~$\Omega$ resistors,
        9~V batteries,
        5~V voltage regulators,
        jumper wires (male to male),
        and assorted LEDs.

    \end{itemize}
\end{description}

\section*{Instructional Sequence}

\begin{itemize}
  \item[5 mins.]
    Facilitators welcome the group and present lesson agenda.

  \item[25 mins.]

  \item[20 mins.]
    Once students feel comfortable with using the breadboard to create
    circuits, facilitators will introduce transistors. For our purpose,
    transistors act as electronic switches which are used to manipulate binary
    values.

    Students will add a transistor to their breadboard. They will do this by
    moving the output of the LED current into the base (middle prong) of the
    transistor. Then they will connect the collector (left prong) to a
    different colour LED and to the positive voltage. Finally the emitter
    (right prong) will connect to the negative voltage.

    Pressing the button of the base wire will light up both the base LED and
    collector LED. Explain this is because the base makes the transistor
    conductive, allowing electricity to move from collector to emitter. The
    base is like a spigot on a tap: when it is open, water flows; when it is
    closed, water does not flow.

  \item[35 mins.]
    When students are comfortable with transistors, they will use 2 transistors
    to make the "and" \& "or" logic gate. To create an and gate using
    transistors, refer to this video:
    \url{https://www.youtube.com/watch?v=sTu3LwpF6XI&t=488s}.

  \item[10 mins.]
\end{itemize}

\end{document}
